---
title: "p8105_hw1_hx2328"
author: "Hao Xu"
date: "2021/9/29"
output: github_document
---

# Problem 1

The creation of data frame:

```{r create_dataframe, message = FALSE}
library(tidyverse)

ex_dataframe = tibble(
  random_sample = rnorm(10),
  logical_vec = random_sample > 0,
  char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  factor_vec = factor(c("study", "eat", "play", "play", "study", "eat", "eat",
                        "play", "play", "study"), 
                      levels = c("study", "eat", "play"))
)
```

The data frame is shown here:

```{r}
ex_dataframe
```

The next step is to try to take mean of each variable:

* The mean of the random sample:

```{r mean1}
mean1 = mean(pull(ex_dataframe, 1))
```

The mean is `r mean1`

* The mean of logical vector:
```{r mean2}
mean2 = mean(pull(ex_dataframe, 2))
```

The mean is `r mean2`

* The mean of character variable:

```{r mean3}
mean3 = mean(pull(ex_dataframe, 3))
```

This time I got a warning message, the variable is not numeric or logical, so R cannot take its mean.

* The mean of factor variable:

```{r mean4}
mean4 = mean(pull(ex_dataframe, 4))
```

This time is the same warning. R cannot take the mean of this variable, and it returns NA.

Then, here is the code chunk as I convert the variables:

```{r convert_variables, eval = FALSE}
conv_logical = as.numeric(pull(ex_dataframe, 2))
conv_char = as.numeric(pull(ex_dataframe, 3))
conv_factor = as.numeric(pull(ex_dataframe, 4))

conv_logical
conv_char
conv_factor
```

This time, the logical variable is converted to number 1 for "TRUE", and number 0 for "FALSE". The character variable is still failed to be converted, and all of them are NA. The factor variales are converted to number 1, 2, or 3 according to their different factor level.


# Problem 2

The process to load the "penguins" dataset:

```{r load_penguins}
data("penguins", package = "palmerpenguins")
```

## Short description of dataset

* The column names of the dataset are: `r colnames(penguins)`

The first column of the dataset is `r colnames(penguins)[1]`, it contains: `r levels(penguins$species)`.

The second column is the `r colnames(penguins)[2]`, it contains: `r levels(penguins$island)`.

The seventh column is `r colnames(penguins)[7]`, it contains: `r levels(penguins$sex)`

The remaining columns are all numerical values describing the attributes of the penguins.

* The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns.

* The mean of the flipper length of those penguins, after removing all NAs, is `r mean(penguins$flipper_length_mm, na.rm = T)` in mm.

## Scatterplot of this dataset

```{r scatterplot_penguins, warning = FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

ggsave("scatter_plot.pdf", height = 4, width = 6)
```

